Tango-cc analysis

### 2024-04-04 stats/analysis.Rmd
work on analyses & plots

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
library(cmdstanr) # modeling
library(janitor) # clean_names
library(ggpubr) # ggarrange
library(splithalfr) # split half reliability
library(ggridges) # for ridge plot
library(RColorBrewer) # for color palette
library(pals) # for color palette

options(scipen = 999) # turn off scientific notation
theme_set(theme_classic()) # set theme

@@

```{r load_data}
complete_data <- read_csv("../data/data.csv")
```

@@

# dataset with test trials only, with mean imprecision per participant
mdata <- data %>%
  summarise(mean_imprecision = mean(imprecision), .by = c(subjid, community, age_group, ageinyears)) %>%
  mutate(age = scale(ageinyears))
```

@@

@@

```{r odd_even_plot}
data %>%
  mutate(half = ifelse(trialnr %% 2 == 0, "half_1", "half_2")) %>%
  group_by(subjid, community, half) %>%
  summarise(mean_imprecision = mean(imprecision)) %>%
  pivot_wider(names_from = half, values_from = mean_imprecision) %>%
  group_by(community) %>%
  summarise(reli = cor(half_1, half_2)) %>%
  ggplot(aes(x = reli, y = community)) +
  geom_vline(xintercept = 0, lty = 3, alpha = .75) +
  geom_point(alpha = .5) +
  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1)) +
  labs(x = "Simple odd-even split") +
  theme_minimal()
```

@@

```{r stratified_targetposition_data}
fn_mean <- function(ds) {
  return(mean(abs(ds$clickdistfromtargetcenterx), na.rm = TRUE))
}

rel <- tibble()

communities <- unique(data$community)

for (j in c(1:50)) {
  for (i in communities) {
    # stratified by target position
    rel_s <- by_split(
      data = data %>% filter(community == i),
      participants = data %>% filter(community == i) %>% pull(subjid),
      fn_score = fn_mean,
      verbose = F,
      stratification = paste(data %>% filter(community == i) %>% pull(centrality)),
      careful = FALSE
      )

    samp <- tibble(
      community = i,
      iter = j,
      reli = split_coefs(rel_s, cor),
      lci = split_ci(rel_s, cor)$lims["0.025","bca"],
      uci = split_ci(rel_s, cor)$lims["0.975","bca"]
      )

    print(i)
    print(j)
    print(rel_s)
    print(samp)

    rel <- bind_rows(rel, samp)
  }
}

saveRDS(rel, "../saves/stratified_internal_consistency.rds")

# rel <- readRDS("../saves/stratified_internal_consistency.rds")
```

```{r stratified_targetposition_plot}
ggplot(rel, aes(x = reli, y = community)) +
  geom_vline(xintercept = 0, lty = 3, alpha = .75) +
  geom_density_ridges(col = "white", alpha = .5,rel_min_height = 0.01,) +
  geom_point(alpha = .5) +
  #geom_pointrange(aes(xmin = lci, xmax = uci)) +
  scale_x_continuous(limits = c(-0.5, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1)) +
  ggtitle("Stratified by target position - no age correction") +
  theme_minimal()
```

## Stratefied and age-corrected

```{r stratified_agecorrected_data}
# estimate age-corrected reliability
# run model first for one community to use update()
split <- split_df(
  data = data %>% filter(community == "Leipzig (Germany)"),
  stratification = data %>% filter(community == "Leipzig (Germany)") %>% pull(centrality),
  careful = FALSE
)

sdata <- bind_rows(
  split[[1]] %>% 
    select(subjid, ageinyears, clickdistfromtargetcenterx) %>% 
    mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
  split[[2]] %>% 
    select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
    mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
  mutate(age = scale(ageinyears))

reli_age <- brm(impr ~ age + (0 + half | subjid),
                data   = sdata,
                family = lognormal(),
                warmup = 1000,
                iter   = 3000,
                control = list(adapt_delta = 0.95),
                chains = 4,
                cores  = 4)

# loop over communities
communities <- unique(data$community)

model_cor <- tibble()

for (j in c(1:50)) {
  for (i in communities) {

    com_split <- split_df(
      data = data %>% filter(community == i),
      stratification = data %>% filter(community == i) %>% pull(centrality),
      careful = FALSE
    )

    com_sdata <- bind_rows(
      com_split[[1]] %>% 
        select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
        mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
      com_split[[2]] %>%
        select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
        mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
      mutate(age = scale(ageinyears))

    com_mod <- update(reli_age,
        newdata = com_sdata,
        warmup = 1000,
        iter   = 3000,
        control = list(adapt_delta = 0.95),
        chains = 4,
        cores  = 4)

    cor <- summary(com_mod)$random$subjid %>%
      as_tibble(rownames = "parameter") %>%
      filter(parameter == "cor(halfhalf_1,halfhalf_2)") %>%
      mutate(community = i, iter = j)

    model_cor <- bind_rows(model_cor, cor)
  }
}

saveRDS(model_cor, "../saves/age_corrected_internal_consistency.rds")

# model_cor <- readRDS("../saves/age_corrected_internal_consistency.rds")  
```

```{r stratified_agecorrected_plot}
ggplot(model_cor, aes(x = Estimate, y = community)) +
  geom_vline(xintercept = 0, lty = 3, alpha = .75) +
  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01,) +
  geom_point(alpha = .5) +
  #geom_pointrange(aes(xmin = `l-95% CI`, xmax = `u-95% CI`), alpha = .5) +
  ggtitle("Stratified by target position - model-based age correction") +
  scale_x_continuous(limits = c(-1, 1), breaks = c(-0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1)) +
  theme_minimal()
```

### run until here

```{r beautified_plot}
model_cor <- model_cor %>% 
    mutate(continent = ifelse(
    community %in% c("leipzig", "plymouth"), "Europe", 
    ifelse(
      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "Americas",
             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
    )
  )) %>%
  mutate(continent = factor(continent, levels = c("Americas", "Africa", "Europe", "Asia", "Oceania"), ordered = T)) %>%
  mutate(community = recode(community,
                            akure = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Zambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            beijing = "Beijing (China)", 
                            india = "Pune (India)",
                            buenos_aires = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Türkiye)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "BaYaka (Rep. Congo)", 
                            uganda = "Nyabyeya (Uganda)")
  )

model_cor %>% 
  ggplot(., aes(x = Estimate, y = community)) +
  geom_vline(xintercept = 0, lty = 3, alpha = .75) +
  geom_density_ridges(col = "white", alpha = .5, rel_min_height = 0.01, fill="#29485D") +
  geom_point(alpha = .5) +
  #geom_pointrange(aes(xmin = `l-95% CI`, xmax = `u-95% CI`), alpha = .5) +
  # ggtitle("Stratified by target position - model-based age correction") +
  scale_x_continuous(limits = c(-1, 1), breaks = c(-1, -0.5, 0, 0.5, 0.6,0.7, 0.8, 0.9, 1)) +
  theme_light() +
  labs(y = "", x = "Splithalf reliability estimate", caption = "(stratified by target position; model-based age correction)")

ggsave("../figures/splithalf_stratified_agecorrected.png", width = 8, height = 5, scale = 1)
```

```{r scatterplot}
data %>% 
  ggplot() +
  geom_point(aes(x = ageinyears, y = mean_click, col = community), alpha = 0.9) +
  scale_color_manual(values = custom_palette) +
  scale_x_continuous(limits = c(2, 11), breaks = seq(2, 11, 1)) +
  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
  labs(x = "Age in years", y = "Average absolute imprecision in target width", col = "")

ggsave("../figures/age_imprecision.png", width = 8, height = 5, scale = 1)
```

```{r ind_diff}
data %>% 
  summarise(mean_click = mean(click), .by = c(community, ageinyears, subjid)) %>%
  ggplot(aes(x = community, y = mean_click, col = ageinyears)) +
  geom_jitter(width = 0.2, height = 0.2, size = 0.9, alpha = 0.9) +
  scale_color_viridis_c(direction = -1) +
  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1), 
    plot.margin = margin(l = 25)
  ) +
  labs(x = "", y = "Average absolute imprecision in target width", col = "Age in years")

ggsave("../figures/ind_diff.png", width = 8, height = 5, scale = 1)
```

```{r dev_trajectory}
dev_model <- brm(impr ~ age + (0 + half | subjid),
                data   = mdata,
                family = lognormal(),
                warmup = 1000,
                iter   = 3000,
                control = list(adapt_delta = 0.95),
                chains = 4,
                cores  = 4)

full_model <- brm(mean_click ~ ageinyears + touchscreen + household + (ageinyears + touchscreen + household | community), 
                              data   = mdata, 
                              family = "lognormal",
                              warmup = 2000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4) %>% 
  add_criterion(., c("waic","loo"))
```

```{r samplesize_plot}
# load source code for geom_flat_violin()
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
library(Hmisc)

plot_data %>% 
  summarise(click = mean(click), .by = c(community, ageinyears)) %>%
  ggplot(mapping = aes(x = community, 
                     y = ageinyears, 
                     fill = community)) + 
  geom_flat_violin(scale = "count", trim = T) + 
  geom_dotplot(binaxis = "y",
               dotsize = 1,
               stackdir = "down",
               binwidth = 0.1,
               position = position_nudge(-0.025)) +
  guides(fill = "none") +
  scale_y_continuous(limits = c(2, 11), breaks = seq(2, 11, 1)) + 
  labs(x = "", y = "Age in years") + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  scale_fill_manual(values = custom_palette)

```{r u_plot}
clicks_bin <- plot_data %>%
  mutate(targetposition = factor(targetposition, levels = c(1:10))) %>%
  group_by(community, targetposition) %>%
  tidyboot_mean(column = click)

clicks_bin %>% 
  ggplot(aes(x = targetposition, y = mean, col = community)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), pch = 20, alpha = 1, position = position_dodge(width = .5)) +
  labs(x = "Target position (binned)", y = "Average absolute imprecision in target width", col = "") +
  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
  scale_color_manual(values = custom_palette) +
  scale_fill_manual(values = custom_palette)

ggsave("../figures/target_position.png", width = 8, height = 4, scale = 1.1)
```

```{r training_plot}
data %>% 
  mutate(trialtype = recode(trialtype, touch = "Training 1", fam = "Training 2", test = "Test") %>% as_factor(.)) %>% 
  na.omit() %>% 
  summarise(mean_click = mean(click), .by = c(community, subjid, ageinyears, trialtype)) %>%
  ggplot(aes(x = community, y = mean_click, col = ageinyears)) +
  geom_jitter(width = 0.25, size = 0.9, alpha = 0.9) +
  scale_color_viridis_c(direction = -1) +
  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1), 
    plot.margin = margin(l = 25)
  ) +
  facet_wrap(~trialtype, ncol = 1) +
  labs(x = "", y = "Average absolute imprecision in target width", col = "Age in years")

ggsave("../figures/training.png", width = 11, height = 5, scale = 1)
```

```{r per_culture_plot}
# function to suppress labels
delete_no_display <- function(v) {
  if_else(str_detect(v, 'no_display'), '', v)
}

data %>% 
  mutate(trialtype = recode(trialtype, touch = "Training 1", fam = "Training 2", test = "Test") %>% as_factor(.)) %>%
  na.omit() %>%
  summarise(mean_click = mean(click), .by = c(continent, community, subjid, ageinyears, trialtype)) %>% 
  mutate(
    continent = fct_inorder(continent) %>% fct_rev(.), 
    # so that first facet row doesnt show x axis labels
    trialtype = if_else(continent == "Africa",
                              as.character(trialtype),
                              paste0(as.character(trialtype), 'no_display')) %>% as_factor(.) %>% fct_relevel(., "Training 1", "Training 2", "Test")
  ) %>%
  ggplot(aes(x = trialtype, y = mean_click, col = ageinyears)) +
  geom_jitter(width = 0.2, size = 0.9, alpha = 0.9) +
  scale_color_viridis_c(direction = -1) +
  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
  theme_light() +
  facet_wrap(~ continent * community, nrow = 2, scales="free_x") +
    theme(
    axis.text.x = element_text(angle = 30, hjust = 1), 
    legend.position = c(0.95, 0.25), 
    axis.ticks.x = element_blank(),
  ) +
  scale_x_discrete(label = delete_no_display) +
  labs(x = "", y = "Average absolute imprecision in target width", col = "Age in years")

ggsave("../figures/per_culture.png", width = 11, height = 5, scale = 1.3)
```

```{r sd_plot}
sd_df <- data %>% 
  add_row(community = "OVERALL") %>% 
  summarise(sd_ind = sd(click), .by = c(community, subjid, ageinyears, mean_click)) %>%
  mutate(
    mean_community = mean(mean_click, na.rm = TRUE),
    sd_community = sd(mean_click, na.rm = TRUE),
    .by = community
  ) %>%
  mutate(sd_overall = sd(mean_community, na.rm = TRUE), facet = ifelse(community == "OVERALL", "OVERALL", "COMMUNITY"))

# plot sd of individual and community means
sd_df %>% 
  ggplot() +
  geom_jitter(data = sd_df %>%  filter(facet == "COMMUNITY"), aes(x = community, y = sd_ind, col = ageinyears), width = 0.1, size = 0.9, alpha = 0.5) +
  geom_point(data = sd_df %>%  filter(facet == "COMMUNITY"), aes(x = community, y = sd_community), size = 3, pch = 18) +
  geom_point(data = sd_df %>%  filter(facet == "OVERALL"), aes(x = "OVERALL", y = sd_overall), size = 5, pch = 18, color = "purple") +
  facet_grid(~ facet, scales = "free", space = "free") +
  scale_color_viridis_c(direction = -1) +
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1), 
    plot.margin = margin(l = 25), 
    strip.text = element_blank()
  ) +
  labs(x = "", y = "Standard deviation of clicks", col = "Age in years")

ggsave("../figures/sd_plot.png", width = 10, height = 5, scale = 1)
```

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
library(cmdstanr) # modeling
library(janitor) # clean_names
library(ggpubr) # ggarrange
library(splithalfr) # split half reliability
library(ggridges) # for ridge plot
library(RColorBrewer) # for color palette
library(pals) # for color palette
library(Hmisc) # for kelly color palette
library(ggrepel) # for geom_text_repel
# load source code for geom_flat_violin()
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

options(scipen = 999) # turn off scientific notation
theme_set(theme_light()) # set theme

@@

```{r load_data}
complete_data <- read_csv("../data/data.csv") %>% 
  mutate(age_group = floor(ageinyears))
```

@@

# dataset with test trials only, with mean imprecision per participant
# scale age across communities; mean_imprecision per subjid; household, touchscreen scaled per community
mdata <- data %>%
  mutate(age = scale(ageinyears, center = T, scale = F)) %>%
  group_by(subjid, community, age_group, ageinyears, age, household, touchscreen) %>%
  summarise(mean_imprecision = mean(imprecision)) %>%
  group_by(community) %>%
  mutate(
    household = scale(household), 
    touchscreen = factor(touchscreen),
  ) %>%
  na.omit()
```

# Sample

@@

```{r samplesize_table}
# sample size table
sample_table <- data %>%
  group_by(community, age_group) %>%
  summarise(n = n_distinct(subjid)) %>%
  arrange(age_group) %>% 
  pivot_wider(names_from = age_group, values_from = n) %>% 
  arrange(community) %>%
  rename(Community = community) %>% 
  replace(is.na(.), 0) %>% 
  # total per community added as column
  mutate(Total = sum(across(where(is.numeric)))) %>% 
  ungroup() %>% 
  # total per age added as row
  bind_rows(summarise(.,
                      across(where(is.numeric), sum),
                      across(where(is.character), ~"Total")))

saveRDS(sample_table, "../saves/sample_table.rds")
```

```{r samplesize_plot}
data %>% 
  summarise(click = mean(imprecision), .by = c(community, ageinyears)) %>%
  ggplot(mapping = aes(x = community, y = ageinyears)) + 
  geom_flat_violin(scale = "count", trim = T, fill = "#29485D", alpha = 0.75) + 
  geom_dotplot(binaxis = "y",
               dotsize = 1,
               stackdir = "down",
               binwidth = 0.1,
               position = position_nudge(-0.025), 
               fill = "#ffffff"
               ) +
  scale_y_continuous(limits = c(2, 11), breaks = seq(2, 11, 1)) + 
  labs(x = "", y = "Age in years") + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

# Variation

```{r model_density}
age_model <- brm(mean_imprecision ~ age + (1 | subjid),
                data   = mdata,
                family = lognormal(),
                warmup = 2000,
                iter   = 6000,
                control = list(adapt_delta = 0.95),
                chains = 4,
                cores  = 4)

age_model

nd <- mdata %>% 
  select(-c(mean_imprecision))

# extract model predictions for mock data
pred_agecorrected <- fitted(age_model, newdata = nd, re_formula = NA) %>% as_tibble() %>% bind_cols(mdata)

density_plot <- pred_agecorrected %>% 
  ggplot(aes(x = Estimate, y = fct_rev(community))) +
  geom_density_ridges(
    jittered_points = TRUE,
    position = position_points_jitter(width = 0.05, height = 0),
    point_shape = '|', point_size = 2, point_alpha = 1, point_color = "#ffffff",
    alpha = 1,
    fill = "#29485D", 
    col = "#ffffff", 
    scale = 1.5
  ) +
  labs(x = "Absolute imprecision in target width", y = "", fill = "Community") +
  expand_limits(y = c(1, 18.5)) + 
  scale_x_continuous(limits = c(0.5, 4), breaks = seq(0, 4, 0.5)) +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())

density_plot
```

```{r training_trials}
# function to suppress labels
delete_no_display <- function(v) {
  if_else(str_detect(v, 'no_display'), '', v)
}

training_trials_plot <- all_trials %>% 
  mutate(trialtype = recode(trialtype, touch = "Training 1", fam = "Training 2", test = "Test") %>% as_factor(.)) %>%
  na.omit() %>%
  summarise(mean_click = mean(imprecision), .by = c(community, subjid, ageinyears, trialtype)) %>% 
  mutate(
    # so that first facet row doesnt show x axis labels
    trialtype = if_else(community %in% c("Leipzig (Germany)", "Malatya (Türkiye)", "Nyabyeya (Uganda)", "Ocuilan (Mexico)", "Plymouth (UK)", "Pune (India)", "Stanford (USA)", "Windhoek (Namibia)"),
                              as.character(trialtype),
                              paste0(as.character(trialtype), 'no_display')) %>% as_factor(.) %>% fct_relevel(., "Training 1", "Training 2", "Test")
  ) %>%
  ggplot(aes(x = trialtype, y = mean_click, col = ageinyears)) +
  geom_jitter(width = 0.2, size = 0.7, alpha = 0.7) +
  scale_color_viridis_c(direction = -1) +
  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
  facet_wrap(~ community, nrow = 2, scales="free_x") +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1), 
    legend.position = c(0.96, 0.25), 
    axis.ticks.x = element_blank(),
    strip.text.x = element_text(size = 7.5), 
    legend.title = element_text(size = 8),
  ) +
  scale_x_discrete(label = delete_no_display) +
  labs(x = "", y = "Average absolute imprecision in target width", col = "Age in years")

training_trials_plot
```

```{r icc}
within_person <- data %>%
  group_by(subjid) %>%
  summarise(
    mean = mean(imprecision, na.rm = TRUE),
    sd = sd(imprecision, na.rm = TRUE),
    var = var(imprecision, na.rm =TRUE),
  )

within_person
saveRDS(within_person, "../saves/within_person.rds")

# proportion of between-community variance relative to the sum of within-community and between-community variance
# generally: ICC = (variance of interest) / (total variance) = (variance of interest) / (variance of interest + unwanted variance)
var_df <- data %>%
  group_by(subjid, community) %>%
  summarise(
    person_mean = mean(imprecision, na.rm = TRUE),
  ) %>% 
  group_by(community) %>%
  summarise(
    community_mean = mean(person_mean),
    community_sd = sd(person_mean),
    within_community_var = var(person_mean)
  ) %>% 
  mutate(
    between_community_var= var(community_mean),
    total_var = between_community_var + sum(within_community_var),
    ICC_b= between_community_var / total_var, 
    ICC_w = sum(within_community_var) / total_var
  ) %>% 
  mutate(across(where(is.numeric), ~round(., 2)))

var_df
saveRDS(var_df, "../saves/var_df.rds")
```

@@

```{r odd_even_plot}
int_con <- data %>%
  mutate(half = ifelse(trialnr %% 2 == 0, "half_1", "half_2")) %>%
  group_by(subjid, community, half) %>%
  summarise(mean_imprecision = mean(imprecision)) %>%
  pivot_wider(names_from = half, values_from = mean_imprecision) %>%
  group_by(community) %>%
  summarise(odd_even = cor(half_1, half_2))

odd_even_plot <- int_con %>% 
  left_join(data %>% group_by(community) %>% summarise(n= n_distinct(subjid))) %>% 
  ggplot(aes(x = odd_even, y = fct_rev(community))) + 
  geom_point(aes(size = n), col = "#29485D", alpha = 1) + 
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_size(limits = c(20, 160), breaks = seq(25, 150, 50)) + 
  labs(y = "", x = "Odd-even split") +
  theme(
    legend.position = c(0.2, 0.2),
    strip.text = element_text(face = "bold", size = 10), 
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 8), 
    legend.box.background = element_rect(), 
    legend.key.height = unit(0.4, "cm"),
    legend.key.width = unit(-1.2, "cm"),
  ) +
  expand_limits(y = c(1, 18.5))

odd_even_plot
```

@@

```{r stratified_data}
# fn_mean <- function(ds) {
#   return(mean(abs(ds$clickdistfromtargetcenterx), na.rm = TRUE))
# }
# 
# strat <- tibble()
# 
# communities <- unique(data$community)
# 
# for (j in c(1:50)) {
#   for (i in communities) {
#     # stratified by target position
#     strat_s <- by_split(
#       data = data %>% filter(community == i),
#       participants = data %>% filter(community == i) %>% pull(subjid),
#       fn_score = fn_mean,
#       verbose = F,
#       stratification = paste(data %>% filter(community == i) %>% pull(centrality)),
#       careful = FALSE
#       )
#     
#     samp <- tibble(
#       community = i,
#       iter = j,
#       reli = split_coefs(strat_s, cor),
#       lci = split_ci(strat_s, cor)$lims["0.025","bca"],
#       uci = split_ci(strat_s, cor)$lims["0.975","bca"]
#       )
#     
#     print(i)
#     print(j)
#     print(strat_s)
#     print(samp)
#     
#     strat <- bind_rows(strat, samp)
#   }
# }

# saveRDS(strat, "../saves/stratified_internal_consistency.rds")

strat <- readRDS("../saves/stratified_internal_consistency.rds")
```

```{r stratified_plot}
stratified_plot <- strat %>%   
  ggplot(., aes(x = reli, y = fct_rev(community))) +
  geom_density_ridges(col = "white", alpha = 1, rel_min_height = 0.01, fill="#29485D") +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(y = "", x = "Stratified by target centrality") +
  theme(axis.title.x = element_text(size = 10)) +
  expand_limits(y = c(1, 18.5))

stratified_plot
```

## Stratified and age-corrected

```{r stratified_agecorrected_data}
# estimate age-corrected reliability
# run model first for one community to use update()
# split <- split_df(
#   data = data %>% filter(community == "Leipzig (Germany)"),
#   stratification = data %>% filter(community == "Leipzig (Germany)") %>% pull(centrality),
#   careful = FALSE
# )
# 
# sdata <- bind_rows(
#   split[[1]] %>% 
#     select(subjid, ageinyears, clickdistfromtargetcenterx) %>% 
#     mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
#   split[[2]] %>% 
#     select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
#     mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
#   mutate(age = scale(ageinyears))
# 
# strat_age_model <- brm(impr ~ age + (0 + half | subjid),
#                 data   = sdata,
#                 family = lognormal(),
#                 warmup = 1000,
#                 iter   = 3000,
#                 control = list(adapt_delta = 0.95),
#                 chains = 4,
#                 cores  = 4)
# 
# # loop over communities
# communities <- unique(data$community)
# 
# strat_age <- tibble()
# 
# for (j in c(1:50)) {
#   for (i in communities) {
#     
#     com_split <- split_df(
#       data = data %>% filter(community == i),
#       stratification = data %>% filter(community == i) %>% pull(centrality),
#       careful = FALSE
#     )
#     
#     com_sdata <- bind_rows(
#       com_split[[1]] %>% 
#         select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
#         mutate(impr = abs(clickdistfromtargetcenterx), half = "half_1"),
#       com_split[[2]] %>%
#         select(subjid, ageinyears, clickdistfromtargetcenterx) %>%
#         mutate(impr = abs(clickdistfromtargetcenterx), half = "half_2")) %>%
#       mutate(age = scale(ageinyears))
#     
#     com_mod <- update(strat_split_model,
#         newdata = com_sdata,
#         warmup = 1000,
#         iter   = 3000,
#         control = list(adapt_delta = 0.95),
#         chains = 4,
#         cores  = 4)
#     
#     cor <- summary(com_mod)$random$subjid %>%
#       as_tibble(rownames = "parameter") %>%
#       filter(parameter == "cor(halfhalf_1, halfhalf_2)") %>%
#       mutate(community = i, iter = j)
#     
#     strat_age <- bind_rows(strat_age, cor)
#   }
# }
# 
# saveRDS(strat_age, "../saves/age_corrected_internal_consistency.rds")

strat_age <- readRDS("../saves/age_corrected_internal_consistency.rds")
```

```{r stratified_agecorrected_plot}
stratified_agecorrected_plot <- strat_age %>% 
  ggplot(., aes(x = Estimate, y = fct_rev(community))) +
  geom_density_ridges(col = "white", alpha = 1, rel_min_height = 0.01, fill="#29485D") +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(y = "", x = "Stratified & age-corrected") +
  theme(axis.title.x = element_text(size = 10)) +
  expand_limits(y = c(1, 18.5))

stratified_agecorrected_plot
```

```{r combine_data}
int_con <- full_join(
  int_con, 
  strat %>% 
    group_by(community) %>%
    summarise(stratified = mean(reli, na.rm = T))
) %>% 
  full_join(
    strat_age %>% 
      group_by(community) %>%
      summarise(stratified_agecorrected = mean(Estimate, na.rm = T))
  )

int_con
saveRDS(int_con, "../saves/internal_consistency.rds")
```

# Combine plots

```{r combine_plot}
top_row <- ggarrange(
  density_plot,
  odd_even_plot,
  stratified_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
  stratified_agecorrected_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
  widths = c(1.5, 2.1, 1.4, 1.4), 
  nrow = 1,
  labels = c("B", "C", "D", "E") 
)

ggarrange(
  training_trials_plot,
  top_row,
  nrow = 2,
  heights = c(2.2, 1.4),
  labels = c("A", "") 
)

ggsave("../figures/tango-cc.png", width = 12, height = 8, scale = 1, bg = "white")
```

# Exploratory: Correlation SD and internal consistency

```{r sd_int_plot}
sd_int_plot <- var_df %>%  
  select(community, community_sd) %>% 
  full_join(int_con) %>% 
  ggplot(aes(x = community_sd, y = stratified_agecorrected)) +
  geom_point(shape = 4, size = 2) +
  geom_smooth(method = "lm", se = FALSE, col = "#29485D") +
  stat_cor(aes(label = paste(..r.label..)), method = "pearson", size = 4, r.accuracy = 0.01, cor.coef.name = "r", label.x = 0.25, label.y = 0.95) +
  scale_x_continuous(limits = c(0.25, 2), breaks = seq(0, 2, 0.5)) +
  scale_y_continuous(limits = c(0.25, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = "Community SD", y = "Internal consistency")

sd_int_plot
```
